MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-17 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
remove arbitrary cutoff number

# Get differential expression
DE = lapply(glue::glue("L{1:6}"), function(i, FIT){
  topTable(FIT, coef=i, number = 50000) %>%
    rownameToFirstColumn('gene_id') %>% 
    left_join(backgroundGenes)
}, FIT.CONTR) 
names(DE) = colnames(contrast)

>>>>

# Get differential expression
DE = lapply(glue::glue("L{1:6}"), function(i, FIT){
  topTable(FIT, coef=i, number = Inf) %>%
    rownameToFirstColumn('gene_id') %>% 
    left_join(backgroundGenes)
}, FIT.CONTR) 
names(DE) = colnames(contrast)
